A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2025-02-14 paper_v02/article.tex
paper version 02

\begin{enumerate}
  \label{steps:DCCA}
  \item Taking two time series with the same length $\{x\alpha_{i}\}$ and $\{x\beta_{i}\}$ with $i$ ranging from $1$ to $N$,
        the integrated series $X\alpha_{k}$ and $X\beta_{k}$ are calculated by
        $X_{k} = \sum_{i=1}^{k}\left[x_{i} - \langle x \rangle \right] $ for each series, with $k$ also ranging from $i$ to $N$;
  \item $X\alpha_{k}$ and $X\beta_{k}$ series are divided in $N - n$ boxes of size $n$(time scale), each box containing $n + 1$ values, starting in $i$ up to $i + n$;
  \item for each box, a polynomial (usually of degree 1) best fit is calculated, getting
        $\widetilde{X\alpha}_{k, i}$ and $\widetilde{X\beta}_{k, i}$,
        for series $\{x\alpha_{i}\}$ and $\{x\beta_{i}\}$ respectively,
        with $i \le k \le (i + n)$;
  \item in each box is calculated: $f_{DCCA}^{2}(n, i) =
          \frac{1}{1+n} \sum_{k=i}^{i + n}(X\alpha_{k}-\widetilde{X\alpha}_{k, i}) \times (X\beta_{k}-\widetilde{X\beta}_{k})$
  \item for all the boxes of a time scale, the $DCCA$ is calculated as:\\[10pt]
        $F_{DCCA}^{2}(n) =\frac{1}{N - n} \sum_{i=1}^{N-n} f_{DCCA}^{2}(n, i)$;
  \item for a number of different timescales ($n$), with possible values
        $4 \le n \le \frac{N}{4}$ the $F_{DCCA}^{2}$ function is calculated to find a relation among
        $F_{DCCA}^{2} \times n$
\end{enumerate}

@@

The function also calls the \verb"detrended()" function, that calculates the $DV$ for each time series. The function is called for every time series in the \verb"MainOperator" structure. The \verb"detrended()" function is not shown in the code above, but it is a simple function that calculates the $DV$ for a time series. The function is called for every time series in the \verb"MainOperator" structure. The \verb"detrended()" function is not shown in the code above, but it is a simple function that calculates the $DV$ for a time series. The function is called for every time series in the \verb"MainOperator" structure. The \verb"detrended()" function is not shown in the code above, but it is a simple function that calculates the $DV$ for a time series. The function is called for every time series in the \verb"MainOperator" structure. The \verb"detrended()" function is not shown in the code above, but it is a simple function that calculates the $DV$ for a time series. The function is called for every time series in the \verb"MainOperator" structure. The \verb"detrended()" function is not shown in the code above, but it is a simple function that calculates the $DV$ for a time series. The function is called for every time series in the \verb"MainOperator" structure. The \verb"detrended()" function is not shown in the code above, but it is a simple function that calculates the $DV$ for a time series. The function is called for every time series in the \verb"MainOperator" structure. The \verb"detrended()" function is not shown in the code above, but it is a simple function that calculates the $DV$ for a time series

>>>>

\begin{enumerate}
  \label{steps:DCCA}
  \item Taking two time series with the same length $\{x\alpha_{i}\}$ and $\{x\beta_{i}\}$ with $i$ ranging from $1$ to $N$,
        the integrated series $X\alpha_{k}$ and $X\beta_{k}$ are calculated by
        $X_{k} = \sum_{i=1}^{k}\left[x_{i} - \langle x \rangle \right] $ for each series, with $k$ also ranging from $i$ to $N$;
  \item $X\alpha_{k}$ and $X\beta_{k}$ series are divided in $N - n$ boxes of size $n$(time scale), each box containing $n + 1$ values, starting in $i$ up to $i + n$;
  \item for each box, a polynomial (usually of degree 1) best fit is calculated, getting
        $\widetilde{X\alpha}_{k, i}$ and $\widetilde{X\beta}_{k, i}$,
        for series $\{x\alpha_{i}\}$ and $\{x\beta_{i}\}$ respectively,
        with $i \le k \le (i + n)$;
  \item in each box is calculated: $f_{DCCA}^{2}(n, i) =
          \frac{1}{1+n} \sum_{k=i}^{i + n}(X\alpha_{k}-\widetilde{X\alpha}_{k, i}) \times (X\beta_{k}-\widetilde{X\beta}_{k})$
  \item for all the boxes of a time scale, the $DCCA$ is calculated as:\\[10pt]
\end{enumerate}

@@

\begin{equation}
\sum_{k=i}^{i + n}S_k = \sum_{j=i-1}^{n}S_j - S_{i-1} + S_{n+1}
\end{equation}
